HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
put the contents of the omitted point in one extra sentence

The German translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

@@

\paragraph{Alignment.}
In HMEANT, the alignment between the reference and translation structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
\newcite{bojar:wu:ssst:2012} and \newcite{chuchunkov-tarelkin-galinskaya:2014:SSST-8}
argue that the structures of the reference and of an accurate translation
may still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow modifications to
the SRL annotations at the alignment stage,
to avoid unduly penalizing such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue is noted in \parcite{lo:wu:reliability:2014}:
the IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.
HUME uses automatic (word-level) alignment, which only
serves as a cue for directing the attention of the annotators.
The user is expected to mentally correct the
alignment as needed, thus circumventing this difficulty.

@@

\com{
\paragraph{Error Localisation.}
In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural units,
which supports a more accurate aggregation of the translation errors
to a composite score.
}
%\oa{Omitted point here}

>>>>

The German translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.
%
Conversely, HMEANT does not allow to penalize errors such as tense or negation
flip in a correctly aligned predicate.

@@

\paragraph{Alignment.}
In HMEANT, the alignment between the reference and translation structures is a key
part of the manual annotation. If the alignment cannot be created, the 
translation is heavily penalized.
\perscite{bojar:wu:ssst:2012} and \perscite{chuchunkov-tarelkin-galinskaya:2014:SSST-8}
argue that the structures of the reference and of an accurate translation
may still diverge, for instance due to a different
interpretation of a PP-attachment, or the verb having an additional modifier in
%suggested that sometimes, the structures of the reference and candidate
%translations diverge without any good reason, for instance due to a different
%interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow modifications to
the SRL annotations at the alignment stage,
to avoid unduly penalizing such spurious divergences.
%annotations also at the alignment stage
%to avoid unduly penalization due to such a spurious divergence.
The same issue is noted by \perscite{lo:wu:reliability:2014}:
the IAA on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.
HUME uses automatic (word-level) alignment, which only
serves as a cue for directing the attention of the annotators.
The user is expected to mentally correct the
alignment as needed, thus circumventing this difficulty.

@@

\com{
\paragraph{Error Localisation.}
In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural units,
which supports a more accurate aggregation of the translation errors
to a composite score.
}
%\oa{Omitted point here} % OB: Added a sentence covering it: Conversely,
%HMEANT does not...
